---
title: "Annual Report"
output: html_document
---

## Conservation Area

`r params$mpas`

## At-a-glance

```{r, echo=FALSE,comment=NA, results="asis"}
library(leaflet)
last_year <- paste0((as.numeric(format(Sys.time(), "%Y"))-1),"-", format(Sys.time(), "%Y"))
string <- state$mpas
if (!(length(Context[[string]]) == 0)) {
cat(Context[[string]])
} else {
  cat("There is no available context for this area.")
}
```


```{r, echo=FALSE, comment=NA, results="asis"}
cat("<div style='display: flex; gap: 10px;'>")
PALETTE <- append(flowerPalette,list("NA" = "#EDEDED"))
for (name in names(PALETTE)) {
  color <- PALETTE[name]
  cat(sprintf("<div style='width: 50px; height: 20px; background-color: %s; text-align: center; 
               color: black; border: 1px solid #000; line-height: 20px;'>%s</div>", 
               color, name))
}
cat("</div>")
```

## Network Conservation Objectives

```{r, echo=FALSE, comment=NA, results="asis"}
# Initialize empty table
objective_table <- data.frame(
  Objective = character(),
  Flower_Plot_Linkage = character(),
  Rationale = character(),
  stringsAsFactors = FALSE
)

filtered_odf <- odf[odf$objectives %in% N_Objectives, ]

for (fo in seq_along(filtered_odf$objectives)) {
  id <- fo
  req(input$mpas %in% c("Scotian Shelf", unique(pillar_ecol_df$areaID)))

  if (state$mpas == "Scotian Shelf") {
    c1 <- 1:length(pillar_ecol_df$areaID)
  } else {
    c1 <- which(pillar_ecol_df$areaID == state$mpas)
  }

  flower_linkage_name <- odf$flower_plot[which(odf$objectives == N_Objectives[id])]

  # Try to match by bin
  c2 <- which(tolower(pillar_ecol_df$bin) == tolower(flower_linkage_name))
  KEEP <- intersect(c1, c2)

  # Fallback: match by objective
  if (length(KEEP) == 0) {
    c2 <- which(tolower(pillar_ecol_df$objective) == tolower(flower_linkage_name))
    KEEP <- intersect(c1, c2)
  }

  flower_linkage <- if (length(KEEP) > 0) {
    unique(pillar_ecol_df$bin[KEEP])[1]
  } else {
    NA
  }

  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  ymax <- weighted.mean(ymax, weight, na.rm = TRUE)

  # Convert score to grade + color
  clc <- as.character(calc_letter_grade(ymax))
  finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
  if (length(finalCol) == 0) finalCol <- "#EDEDED"

  # Add styled objective label and linkage to the table
  objective_table <- rbind(objective_table, data.frame(
    Objective = sprintf(
      '<span style="color:%s; padding:3px; text-shadow: -1px -1px 0 black, 1px -1px 0 black, -1px 1px 0 black, 1px 1px 0 black;"><b>%s</b></span>',
      finalCol, N_Objectives[fo]
    ),
    Flower_Plot_Linkage = flower_linkage,
    Rationale = NA_character_,
    stringsAsFactors = FALSE
  ))
}

# Optional: View in HTML in RMarkdown or render in Shiny
DT::datatable(objective_table, escape = FALSE, rownames = FALSE)


```

## Site Conservation Objectives

```{r, echo=FALSE,comment=NA, results="asis"}
string <- state$mpas
keepO <- string

# Get site-level objectives
S_Objectives <- Objectives_processed[[keepO]]

# Initialize the table
objective_table_site <- data.frame(
  Objective = character(),
  Flower_Plot_Linkage = character(),
  Rationale = character(),
  stringsAsFactors = FALSE
)

if (!(length(S_Objectives) == 0)) {
  filtered_odfS <- odf[odf$objectives %in% S_Objectives, ]

  for (fo in seq_along(filtered_odfS$objectives)) {
    id <- fo
    req(input$mpas %in% c("All", unique(pillar_ecol_df$areaID)))

    # Subset rows by MPA
    if (state$mpas == "All") {
      c1 <- 1:length(pillar_ecol_df$areaID)
    } else {
      c1 <- which(pillar_ecol_df$areaID == state$mpas)
    }

    # Get flower plot linkage name
    flower_linkage_name <- odf$flower_plot[which(odf$objectives == S_Objectives[id])]

    # Special handling for environmental representativity
    if (tolower(flower_linkage_name) == "environmental (representativity)") {
      c2 <- which(tolower(pillar_ecol_df$bin) == "environmental representativity")
    } else {
      c2 <- which(tolower(pillar_ecol_df$bin) == tolower(flower_linkage_name))
    }

    KEEP <- intersect(c1, c2)
    ymax <- pillar_ecol_df$score[KEEP]
    weight <- pillar_ecol_df$weight[KEEP]

    # Fallback match by 'objective' field
    if (length(ymax) == 0) {
      c2 <- which(tolower(pillar_ecol_df$objective) == tolower(flower_linkage_name))
      KEEP <- intersect(c1, c2)
      ymax <- pillar_ecol_df$score[KEEP]
      weight <- pillar_ecol_df$weight[KEEP]
    }

    # Calculate weighted mean
    ymax <- weighted.mean(ymax, weight, na.rm = TRUE)

    # Convert score to grade → color
    clc <- as.character(calc_letter_grade(ymax))
    finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
    if (length(finalCol) == 0) finalCol <- "#EDEDED"

    # Add row to site-level table with HTML color styling
    objective_table_site <- rbind(objective_table_site, data.frame(
      Objective = sprintf(
        '<span style="color:%s; padding:3px; text-shadow: -1px -1px 0 black, 1px -1px 0 black, -1px 1px 0 black, 1px 1px 0 black;"><b>%s</b></span>',
        finalCol, S_Objectives[fo]
      ),
      Flower_Plot_Linkage = flower_linkage_name,
      Rationale = NA_character_,
      stringsAsFactors = FALSE
    ))
  }

  # Render the styled DT table
  DT::datatable(
    objective_table_site,
    escape = FALSE,
    rownames = FALSE,
    options = list(
      dom = 't',         # No filter/search box
      pageLength = 100   # Show all if < 100
    )
  )

} else {
  cat("There are no site objectives pulled with our tools for this area.")
}




```


```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
p <- pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas),]
area_grade <- calc_letter_grade(weighted.mean(p$score, p$weight, na.rm=TRUE))

```

```{r, echo=FALSE}
if (state$mpas %in% MPA_report_card$NAME_E) {
  fill_color <- ifelse(
    is.na(MPA_report_card$grade[which(MPA_report_card$NAME_E == state$mpas)]),
    "#EDEDED",
    flowerPalette[[MPA_report_card$grade[which(MPA_report_card$NAME_E == state$mpas)]]]
  )

  # Set border color conditionally
  border_color <- if (fill_color == "#ABD9E9") "black" else fill_color

  map <- leaflet() %>%
    addTiles() %>%
    addPolygons(
      data = MPAs$geoms[which(MPAs$NAME_E == state$mpas)],
      fillColor = fill_color,
      fillOpacity = 0.5,
      weight = 2,
      color = border_color
    )
  
} else {
  fill_color <- flowerPalette[[area_grade]]
  border_color <- if (fill_color == "#ABD9E9") "black" else fill_color

  map <- leaflet() %>%
    addTiles() %>%
    addPolygons(
      data = MPAs$geoms[which(MPAs$NAME_E == state$mpas)],
      fillColor = fill_color,
      fillOpacity = 0.5,
      weight = 2,
      color = border_color
    )
}


map
```

## Creature Feature

```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
#FIXME - Get from PPT Milestones/Deliverable

if (state$mpas == "St. Anns Bank Marine Protected Area") {
  cat("Scientists have found large numbers of thorny skate or kekunaluej purses (egg capsules) in a part of St. Anns Bank Marine Protected Area")
} else {
  cat("There is no identified creature feature for this area.")
}

```

## Research and Monitoring

### Flower Plot

```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
plot_flowerplot(pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas),],
                                            grouping = "objective",
                                            labels = "bin",
                                            score = "score",
                                            max_score=100,
                                            min_score=0,
                                            title="Flower plot frame work")
```


As shown above, in `r params$mpas` the over all grade based on our criteria is `r area_grade` with each bin having the following grade:

```{r, echo=FALSE, comment=NA, results="asis"}
# Create an empty data frame to store results
summary_table <- data.frame(
  `Indicator Bin` = character(),
  `Grade` = character(),
  `Number of Indicators` = character(),
  stringsAsFactors = FALSE
)

# Loop through bins and calculate grades
for (i in seq_along(unique(p$bin))) {
  keep <- which(p$bin == unique(p$bin)[i])
  df <- p[keep, ]
  
  grade <- calc_letter_grade(weighted.mean(df$score, df$weight, na.rm = TRUE))
  
  if (any(is.na(df$indicator) | df$indicator == "placeholder" | is.na(df$score))) {
  indicatorLength <- length(df$indicator[-which(is.na(df$indicator) | df$indicator == "placeholder" | is.na(df$score))])
  } else {
    indicatorLength <- length(df$indicator)
  }
  
  summary_table[i, ] <- c(unique(p$bin)[i], grade, indicatorLength)
}

# Print as a table
print(knitr::kable(summary_table, caption = "Grades by Indicator Bin"))


```


```{r, echo=FALSE, comment=NA, results="asis"}
library(knitr)
library(leaflet)

image_folder <- file.path(Sys.getenv("OneDriveCommercial"),
                                    "MarConsNetTargets","data",
                                    "plots")
image_files <- list.files(image_folder, full.names = TRUE)

keeper <- pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas), ]

BINS <- unique(trimws(tolower(unlist(
  strsplit(keeper$bin, ";")
)), "both"))


keeper2 <- NULL

for (i in seq_along(BINS)) {
  KK <- keeper[which(grepl(BINS[i], trimws(tolower(
    keeper$bin
  ), "both"))), ]
  
  # Remove NA and placeholder indicators
  
  if (any(is.na(KK$indicator) | KK$indicator == "placeholder" | is.na(KK$score))) {
    KK <- KK[-(which(is.na(KK$indicator) | KK$indicator == "placeholder" | is.na(KK$score))),]
  }
  
  keeper2[[i]] <- data.frame(
    Indicator = KK$indicator,
    Status = KK$status_statement,
    Trend = KK$trend_statement,
    #Plot = KK$plot,
    Grade = KK$score,
    Project = KK$PPTID,
    Source = KK$source,
    stringsAsFactors = FALSE
  )
  
}

names(keeper2) <- BINS

for (i in seq_along(keeper2)) {
  cat(sprintf('<details><summary><strong>Indicator Bin: %s</strong></summary>\n\n', toupper(BINS[i])))
  
  if (!(length(keeper2[[i]]$Indicator) == 0)) {
  for (j in seq_along(keeper2[[i]]$Indicator)) {
    cat(sprintf("<b>Indicator: %s.</b>\n\n", keeper2[[i]]$Indicator[j]))
    
    
    # FINDING PLOT
      k1 <- which(grepl(make.names(state$mpas), image_files, ignore.case=TRUE)) # Which are from the correct area
      k2 <- which(grepl(make.names(keeper2[[i]]$Indicator[j]), image_files, ignore.case=TRUE)) # Which ones have the correct indicator name
      KEEP <- intersect(k1,k2)
      
      if (length(KEEP) > 1) {
        KEEP <- KEEP[which(sub(".*_(.*?)\\.png$", "\\1", image_files[KEEP]) == keeper2[[i]]$Indicator[j])]
      }
      plot_file <- image_files[KEEP]
    
    # END PLOT
      if (length(plot_file) > 0) {
      for (p in seq_along(plot_file)) {
        #cat("![](", plot_file[p], ")\n\n", sep = "")
         cat('<img src="', plot_file[p], '" width="600"/>\n\n', sep = "")
      }
      }
      
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf("%s.\n\n", keeper2[[i]]$Status[j]))
      if (is.na(keeper2[[i]]$Trend[j])) {
        cat(sprintf("%s.\n\n", "No temporal analysis completed for this indicator."))
      } else if (!(keeper2[[i]]$Trend[j] == "There is no temporal dimension in this data.")) {
      cat(sprintf("%s.\n\n", keeper2[[i]]$Trend[j]))
      }
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf(
  "This indicator has a score of: %s.\n\nBased on the following scoring scheme: %s\n",
  keeper2[[i]]$Grade[j],
  pillar_ecol_df$scoring[
    which(
      pillar_ecol_df$indicator == keeper2[[i]]$Indicator[j] &
      pillar_ecol_df$areaID == state$mpas
    )
  ]
))

      cat(sprintf("%s.\n\n", " "))
      cat(sprintf(
        "Data was provided from %s.\n\n",
        ifelse(is.na(keeper2[[i]]$Project[j]), keeper2[[i]]$Source[j], keeper2[[i]]$Project[j])
      ))
  } # END HERE
  
  } else {
  cat("There are no indicators in the app for this indicator bin.")
}
  cat("</details>\n\n")
}


```
## Discussion

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

cat("### Climate Change\n")

climate_indicators <- unique(pillar_ecol_df$indicator[which(grepl("Inside", pillar_ecol_df$indicator) & pillar_ecol_df$areaID == state$mpa)])

for (i in seq_along(climate_indicators)) {
  indicator_keep <- which(pillar_ecol_df$indicator == gsub(" Inside Outside Comparison$", "", climate_indicators[i]) & pillar_ecol_df$areaID == state$mpas)
  
  if (!(length(indicator_keep) == 0) & !(is.na(pillar_ecol_df$trend_statement[indicator_keep]))) {
    
    excel_keep <- which(climate$Indicator == climate_indicators[i])
    pillar_keep_inside <- which(pillar_ecol_df$indicator == climate_indicators[i] & pillar_ecol_df$areaID == state$mpas)
    
    cat(sprintf("<b>Indicator: %s.</b>\n\n",toupper(climate_indicators[i])))
    
    cat(climate$Context[excel_keep], "\n\n")
    cat("In our analysis, ")
    cat(pillar_ecol_df$trend_statement[indicator_keep])
    
    if (!(grepl("There is only one year of data", pillar_ecol_df$trend_statement[indicator_keep]))) {
    
    pval <- str_extract(pillar_ecol_df$trend_statement[indicator_keep], "pval\\s*=\\s*\\d+(\\.\\d+)?") |>
      str_extract("\\d+(\\.\\d+)?") |>
      as.numeric()
    
    if (pval > 0.05) {
      cat(". The change in this indicator in the MPA is not significant.")
    } else {
      cat(". The change in this indicator in the MPA is significant.")
    }
    
    cat(" An inside/outside comparison was done to help understand the impacts of climate change on this variable. Results showed ")
    
    result <- pillar_ecol_df$status_statement[pillar_keep_inside]
    
    cat(paste0(tolower(result), "."))
    
    if (!(grepl("Protection could therefore be positively impacting this variable", result))) {
      # No sig dif between the two
      desired <- sub(".*\\s+", "", pillar_ecol_df$scoring[indicator_keep])
      actual_results <- ifelse(grepl("increase", sub("\\..*", ".", pillar_ecol_df$trend_statement[indicator_keep])), "increase", "decrease")
      
      if (pval > 0.05) { ## This is pval of the variable (not inside/ outside)
        cat("The rate in which this indicator is changing is not significant (p=", pval,") which suggests that climate change does not seem to have a significant impact on that particular indicator.")
      } else {
        # change is significant
        if (identical(desired, actual_results)) {
          cat("The results show us that climate change doesn't seem to be impacting this indicator the way we would expect, and in fact, the trends are showing a statistically significant trend in the opposite direction than we would expect.")
        } else {
          #The trend is going in the opposite direction that we would expect and
          #statistically significant,we point out that according to our analysis
          cat("The results show us that climate change could be impacting this indicator the way we would expect, and in fact, the trends are showing a statistically significant
        trend in the direction than we would expect as a result of climate change.")
        }
      }
    }
    } else {
    cat("More sampling is suggested.")
  }
  }
  
  cat("\n\n")
}

cat("### Research Recommendations \n")

cat(paste0(
  "The following indicator bins do not have any data: ",
  paste0(summary_table$Indicator.Bin[which(summary_table$Grade == "NA")], collapse = ", "),
  ". It is recommended to further study these areas.\n"
))
cat("\n\n")

# Bad grade table
badGrade <- which(pillar_ecol_df$areaID == state$mpas & (!(is.na(pillar_ecol_df$indicator))) & (!(pillar_ecol_df$indicator == "placeholder")) & (!(grepl('Inside Outside', pillar_ecol_df$indicator))) & (pillar_ecol_df$score < 51 | is.na(pillar_ecol_df$score)))

badGradeTable <- pillar_ecol_df[badGrade, ] |> 
  dplyr::group_by(bin) |>
  dplyr::ungroup() |>
  dplyr::select("indicator", "score")


cat("The following indicators are scoring low or don't have enough data to properly score. Some additional effort should be considered with these indicators: \n")

print(knitr::kable(badGradeTable, caption = "Indicator to Potentially Further Explore",row.names=FALSE))


```








## Collaborations and partnerships


```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
project_subset <- pillar_ecol_df$PPTID[which(pillar_ecol_df$areaID == state$mpas)]
if (!(length(project_subset) == 0)) {
p_subset <- unique(trimws(unlist(strsplit(project_subset, ";")), "both"))
}
if (any(is.na(p_subset))) {
  p_subset <- p_subset[-which(is.na(p_subset))]
}
if (any(p_subset == "NA")) {
  p_subset <- p_subset[-which(p_subset == "NA")]
}

if (any(p_subset %in% collaborations$project_id)) {
  good_col <- which(collaborations$project_id %in% p_subset)
  collab_subset <- collaborations[good_col,]
  
  ## For collaborations, I need to obtain the year. This would allow me to say 'for this year, x collaborations happened, but in previous years for this project, Y collaborations have happened).
  
  #last_year <- paste0((as.numeric(format(Sys.time(), "%Y"))-1),"-", format(Sys.time(), "%Y"))
  
  year_keep <- which(collab_subset$fiscal_year == last_year)
  
  if (!(length(year_keep) == 0)) {
    recent_col <- collab_subset[year_keep, !(names(collab_subset) %in% c("project_year_id", "new_or_existing", "type", "critical"))]
    names(recent_col) <- c("Project ID", "Organization", "Year")

   organizations <- unique(recent_col$Organization)
    rc <- data.frame(Organization=organizations)
    
    for (i in seq_along(organizations)) {
      keeping <- which(recent_col$Organization == organizations[i])
      rc$Year[i] <- paste0(sort(unique(recent_col[keeping,]$Year)), collapse= ", ")
    }
    cat(paste0("The following collaborations/partnerships were identified for ", last_year, " for projects that contributed to this site:"))
    cat("\n\n")

    print(knitr::kable(rc, caption = "Recent Collaborations and Partnerships",row.names=FALSE))
    cat("\n\n")
  } else {
  cat(paste0("In year ", last_year, " there were no identified collaborations/ partnerships. /n/n"))  
  }
  if (!(length(which((!(1:length(collab_subset$project_id)%in% year_keep))))) == 0) {
    
    cat("The following past partnerships/collaborations have been identified and contributed to this site: \n\n")
    past_coll <- collab_subset[-year_keep, !(names(collab_subset) %in% c("project_year_id", "new_or_existing", "type", "critical"))]
    names(past_coll) <- c("Project ID", "Organization", "Year")
    organizations <- unique(past_coll$Organization)
    pc <- data.frame(Organization=organizations)
    
    for (i in seq_along(organizations)) {
      keeping <- which(past_coll$Organization == organizations[i])
      pc$Year[i] <- paste0(sort(unique(past_coll[keeping,]$Year)), collapse= ", ")
    }

    print(knitr::kable(pc, caption = "Past Collaborations and Partnerships",row.names=FALSE))
    
  } else {
    cat("There are no partnerships/collaborations identified from previous years. \n\n")
  }
} else {
    cat("There have been no identified collaborations/ partnerships for this area using the Project Planning Tool. \n\n")
}
```

## Outreach and engagement

### Deliverables

```{r, echo=FALSE, error=FALSE, warning=FALSE, results='asis'}
deliv_keep <- which(deliverables$project_id %in% p_subset & deliverables$year == last_year) # Only projects for this area / last year

if (length(deliv_keep > 0)) {
  delv <- deliverables[deliv_keep,][c("classification_display", "description")]
  if (any(str_count(delv$description, "\\S+") > 35)) {
  delv$description[which(str_count(delv$description, "\\S+") > 35)] <- " "
  }
  
  names(delv) <- c("Deliverable", "Description")
  
  print(knitr::kable(delv, caption = paste0("Deliverables for " , last_year ),row.names=FALSE))
} else {
  cat("There has been no identified deliverables in the Project Planning Tool for projects supporting this area.")
}

```

### CSAS

```{r, echo=FALSE, error=FALSE, warning=FALSE, results='asis'}
# Which ones to keep
csas_keep <- which(grepl(paste(state$mpas, collapse = "|"), csas$title)) # state$mpas
if (state$mpas == "Western/Emerald Banks Conservation Area (Restricted Fisheries Zone)") {
csas_keep <- c(csas_keep, which(grepl("Emerald Banks", csas$title, ignore.case=TRUE)))
} else if (state$mpas ==  "St. Anns Bank Marine Protected Area") {
  csas_keep <- c(csas_keep, which(grepl("Anns", csas$title, ignore.case=TRUE)))
} else if (state$mpas == "Musquash Estuary Marine Protected Area") {
  csas_keep <- c(csas_keep, which(grepl("Musquash", csas$title, ignore.case=TRUE)))
}

if (length(csas_keep) > 0) {
  CSAS <- csas[csas_keep,]
  names(CSAS) <- c("Title", "Date")
  print(knitr::kable(CSAS, caption = paste0("CSAS Processes for " , state$mpas),row.names=FALSE))
} else {
  cat("There have been no identified relevant CSAS meetings in the CSAS DMapps related to this area.")
}




```

