---
title: "Annual Report"
output: html_document
---

## Conservation Area

`r params$mpas`

## At-a-glance

```{r, echo=FALSE,comment=NA, results="asis"}
last_year <- paste0((as.numeric(format(Sys.time(), "%Y"))-1),"-", format(Sys.time(), "%Y"))
string <- state$mpas
if (!(length(Context[[string]]) == 0)) {
cat(Context[[string]])
} else {
  cat("There is no available context for this area.")
}
```


```{r, echo=FALSE, comment=NA, results="asis"}
cat("<div style='display: flex; gap: 10px;'>")
PALETTE <- append(flowerPalette,list("NA" = "#EDEDED"))
for (name in names(PALETTE)) {
  color <- PALETTE[name]
  cat(sprintf("<div style='width: 50px; height: 20px; background-color: %s; text-align: center; 
               color: black; border: 1px solid #000; line-height: 20px;'>%s</div>", 
               color, name))
}
cat("</div>")
```

## Network Conservation Objectives

```{r, echo=FALSE, comment=NA, results="asis"}
filtered_odf <- odf[odf$objectives %in% N_Objectives, ]

for (fo in seq_along(filtered_odf$objectives)) {
  id <- fo
  req(input$mpas %in% c("Scotian Shelf", unique(pillar_ecol_df$areaID)))
  if (state$mpas == "Scotian Shelf") {
    c1 <- 1:length(pillar_ecol_df$areaID)
  } else {
    c1 <- which(pillar_ecol_df$areaID == state$mpas)
  }
 c2 <- which(tolower(pillar_ecol_df$bin) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
  KEEP <- intersect(c1,c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  if (length(ymax) == 0) {
  # This means it's a ecological objective (i.e. biodiversity, productivity, habitat)
  c2 <- which(tolower(pillar_ecol_df$objective) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
  KEEP <- intersect(c1,c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  }

  #ymax <- ymax[-which(ymax == 0)]
  ymax <- weighted.mean(ymax, weight, na.rm=TRUE)
  # Create data frame for plotting
  data <- data.frame(x = paste0("Objective ", id), y = ymax)
  clc <- as.character(calc_letter_grade(data$y))
  finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
  if (length(finalCol) == 0) {
    finalCol <- "black"
  }
cat(sprintf('<span style="color:%s; background-color:lightgray; padding:3px;"><b>%s</b></span><br>', finalCol, N_Objectives[fo]))
}
```

## Site Conservation Objectives

```{r, echo=FALSE,comment=NA, results="asis"}
string <- state$mpas
keepO <- string


S_Objectives <- Objectives_processed[[keepO]]

if (!(length(S_Objectives) == 0)) {
filtered_odfS <- odf[odf$objectives %in% S_Objectives, ]

for (fo in seq_along(filtered_odfS$objectives)) {
  id <- fo
  req(input$mpas %in% c("All", unique(pillar_ecol_df$areaID)))
  if (state$mpas == "All") {
    c1 <- 1:length(pillar_ecol_df$areaID)
  } else {
    c1 <- which(pillar_ecol_df$areaID == state$mpas)
  }
  
   if (tolower(odf$flower_plot[which(odf$objectives == S_Objectives[id])]) == "environmental (representativity)") {
 c2 <- which(tolower(pillar_ecol_df$bin) == "environmental representativity")

} else {
c2 <- which(tolower(pillar_ecol_df$bin) == tolower(odf$flower_plot[which(odf$objectives == S_Objectives[id])]))
 }
  
  
  KEEP <- intersect(c1, c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  
  # Handling empty or multiple ymax cases
  if (length(ymax) == 0) {
    # This means it's a ecological objective (i.e. biodiversity, productivity, habitat)
    c2 <- which(tolower(pillar_ecol_df$objective) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
    KEEP <- intersect(c1, c2)
    ymax <- pillar_ecol_df$score[KEEP]
    weight <- pillar_ecol_df$weight[KEEP]
  }
  ymax <- weighted.mean(ymax, weight, na.rm = TRUE)
  # Create data frame for plotting
  data <- data.frame(x = paste0("Objective ", id), y = ymax)
  clc <- as.character(calc_letter_grade(data$y))
  finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
  if (length(finalCol) == 0) {
    finalCol <- "black"
  }
cat(sprintf('<span style="color:%s; background-color:lightgray; padding:3px;"><b>%s</b></span><br>', finalCol, S_Objectives[fo]))
}
} else {
  cat("There are no site objectives pulled with our tools for this area.")
}
```


```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
p <- pillar_ecol_df[which(pillar_ecol_df$areaID == string),]
area_grade <- calc_letter_grade(weighted.mean(p$score, p$weight, na.rm=TRUE))

```

```{r, echo=FALSE}

if (string %in% MPA_report_card$NAME_E) {
  fill_color <- ifelse(
    is.na(MPA_report_card$grade[which(MPA_report_card$NAME_E == state$mpas)]),
    "#EDEDED",
    flowerPalette[[MPA_report_card$grade[which(MPA_report_card$NAME_E == state$mpas)]]]
  )

  # Set border color conditionally
  border_color <- if (fill_color == "#ABD9E9") "black" else fill_color

  map <- leaflet() %>%
    addTiles() %>%
    addPolygons(
      data = MPAs$geoms[which(MPAs$NAME_E == state$mpas)],
      fillColor = fill_color,
      fillOpacity = 0.5,
      weight = 2,
      color = border_color
    )
  
} else {
  fill_color <- flowerPalette[[area_grade]]
  border_color <- if (fill_color == "#ABD9E9") "black" else fill_color

  map <- leaflet() %>%
    addTiles() %>%
    addPolygons(
      data = MPAs$geoms[which(MPAs$NAME_E == state$mpas)],
      fillColor = fill_color,
      fillOpacity = 0.5,
      weight = 2,
      color = border_color
    )
}


map
```

## Creature Feature

```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
#FIXME - Get from PPT Milestones/Deliverable

if (state$mpas == "St. Anns Bank Marine Protected Area") {
  cat("Scientists have found large numbers of thorny skate or kekunaluej purses (egg capsules) in a part of St. Anns Bank Marine Protected Area")
} else {
  cat("There is no identified creature feature for this area.")
}


```

## Research and Monitoring

### Flower Plot

```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
plot_flowerplot(pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas),],
                                            grouping = "objective",
                                            labels = "bin",
                                            score = "score",
                                            max_score=100,
                                            min_score=0,
                                            title="Flower plot frame work")
```


As shown above, in `r params$mpas` the over all grade based on our criteria is `r area_grade` with each bin having the following grade:

```{r, echo=FALSE, comment=NA, results="asis"}

# Create an empty data frame to store results
summary_table <- data.frame(
  `Indicator Bin` = character(),
  `Grade` = character(),
  stringsAsFactors = FALSE
)

# Loop through bins and calculate grades
for (i in seq_along(unique(p$bin))) {
  keep <- which(p$bin == unique(p$bin)[i])
  df <- p[keep, ]
  
  grade <- calc_letter_grade(weighted.mean(df$score, df$weight, na.rm = TRUE))
  
  summary_table[i, ] <- c(unique(p$bin)[i], grade)
}

# Print as a table
print(knitr::kable(summary_table, caption = "Grades by Indicator Bin"))


```


```{r, echo=FALSE, comment=NA, results="asis"}
library(knitr)
library(leaflet)

image_folder <- file.path(Sys.getenv("OneDriveCommercial"),
                                    "MarConsNetTargets","data",
                                    "plots")
image_files <- list.files(image_folder, full.names = TRUE)

keeper <- pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas), ]

BINS <- unique(trimws(tolower(unlist(
  strsplit(keeper$bin, ";")
)), "both"))

keeper2 <- NULL

for (i in seq_along(BINS)) {
  KK <- keeper[which(grepl(BINS[i], trimws(tolower(
    keeper$bin
  ), "both"))), ]

  keeper2[[i]] <- data.frame(
    Indicator = KK$indicator,
    Status = KK$status_statement,
    Trend = KK$trend_statement,
    #Plot = KK$plot,
    Grade = KK$score,
    Project = KK$PPTID,
    stringsAsFactors = FALSE
  )
  
}

names(keeper2) <- BINS

for (i in seq_along(keeper2)) {
  #cat(sprintf("### Indicator Bin: %s\n\n", BINS[i]))
  cat(sprintf('<details><summary><strong>Indicator Bin: %s</strong></summary>\n\n', toupper(BINS[i])))
  for (j in seq_along(keeper2[[i]]$Indicator)) {
    cat(sprintf("<b>Indicator: %s.</b>\n\n", keeper2[[i]]$Indicator[j]))
    
    
    # FINDING PLOT
      k1 <- which(grepl(make.names(state$mpas), image_files, ignore.case=TRUE)) # Which are from the correct area
      k2 <- which(grepl(make.names(keeper2[[i]]$Indicator[j]), image_files, ignore.case=TRUE)) # Which ones have the correct indicator name
      KEEP <- intersect(k1,k2)
      plot_file <- image_files[KEEP]
    
    # END PLOT
      if (length(plot_file) > 0) {
      for (p in seq_along(plot_file)) {
        #cat("![](", plot_file[p], ")\n\n", sep = "")
         cat('<img src="', plot_file[p], '" width="400"/>\n\n', sep = "")
      }
      }
      
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf("%s.\n\n", keeper2[[i]]$Status[j]))
      cat(sprintf("%s.\n\n", keeper2[[i]]$Trend[j]))
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf("This indicator has a score of: %s.\n\n", keeper2[[i]]$Grade[j]))
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf(
        "Data was provided from project %s.\n\n",
        keeper2[[i]]$Project[j]
      ))
  }
  cat("</details>\n\n")
}


```


## Collaborations and partnerships


```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
project_subset <- pillar_ecol_df$PPTID[which(pillar_ecol_df$areaID == state$mpas)]
if (!(length(project_subset) == 0)) {
p_subset <- unique(trimws(unlist(strsplit(project_subset, ";")), "both"))
}
if (any(is.na(p_subset))) {
  p_subset <- p_subset[-which(is.na(p_subset))]
}
if (any(p_subset == "NA")) {
  p_subset <- p_subset[-which(p_subset == "NA")]
}

if (any(p_subset %in% collaborations$project_id)) {
  good_col <- which(collaborations$project_id %in% p_subset)
  collab_subset <- collaborations[good_col,]
  
  ## For collaborations, I need to obtain the year. This would allow me to say 'for this year, x collaborations happened, but in previous years for this project, Y collaborations have happened).
  
  #last_year <- paste0((as.numeric(format(Sys.time(), "%Y"))-1),"-", format(Sys.time(), "%Y"))
  
  year_keep <- which(collab_subset$fiscal_year == last_year)
  
  if (!(length(year_keep) == 0)) {
    recent_col <- collab_subset[year_keep, !(names(collab_subset) %in% c("project_year_id", "new_or_existing", "type", "critical"))]
    names(recent_col) <- c("Project ID", "Organization", "Year")

   organizations <- unique(recent_col$Organization)
    rc <- data.frame(Organization=organizations)
    
    for (i in seq_along(organizations)) {
      keeping <- which(recent_col$Organization == organizations[i])
      rc$Year[i] <- paste0(sort(unique(recent_col[keeping,]$Year)), collapse= ", ")
    }
    cat(paste0("The following collaborations/partnerships were identified for ", last_year, " for projects that contributed to this site:"))
    cat("\n\n")

    print(knitr::kable(rc, caption = "Recent Collaborations and Partnerships",row.names=FALSE))
    cat("\n\n")
  } else {
  cat(paste0("In year ", last_year, " there were no identified collaborations/ partnerships. /n/n"))  
  }
  if (!(length(which((!(1:length(collab_subset$project_id)%in% year_keep))))) == 0) {
    
    cat("The following past partnerships/collaborations have been identified and contributed to this site: \n\n")
    past_coll <- collab_subset[-year_keep, !(names(collab_subset) %in% c("project_year_id", "new_or_existing", "type", "critical"))]
    names(past_coll) <- c("Project ID", "Organization", "Year")
    organizations <- unique(past_coll$Organization)
    pc <- data.frame(Organization=organizations)
    
    for (i in seq_along(organizations)) {
      keeping <- which(past_coll$Organization == organizations[i])
      pc$Year[i] <- paste0(sort(unique(past_coll[keeping,]$Year)), collapse= ", ")
    }

    print(knitr::kable(pc, caption = "Past Collaborations and Partnerships",row.names=FALSE))
    
  } else {
    cat("There are no partnerships/collaborations identified from previous years. \n\n")
  }
} else {
    cat("There have been no identified collaborations/ partnerships for this area using the Project Planning Tool. \n\n")
}
```

## Outreach and engagement

### Deliverables

```{r, echo=FALSE, error=FALSE, warning=FALSE, results='asis'}
deliv_keep <- which(deliverables$project_id %in% p_subset & deliverables$year == last_year) # Only projects for this area / last year

if (length(deliv_keep > 0)) {
  delv <- deliverables[deliv_keep,][c("classification_display", "description")]
  if (any(str_count(delv$description, "\\S+") > 35)) {
  delv$description[which(str_count(delv$description, "\\S+") > 35)] <- " "
  }
  
  names(delv) <- c("Deliverable", "Description")
  
  print(knitr::kable(delv, caption = paste0("Deliverables for " , last_year ),row.names=FALSE))
} else {
  cat("There has been no identified deliverables in the Project Planning Tool for projects supporting this area./n/n")
}

```
### CSAS

```{r, echo=FALSE, error=FALSE, warning=FALSE, results='asis'}
# Which ones to keep
csas_keep <- which(grepl(paste(state$mpas, collapse = "|"), csas$title)) # state$mpas
if (state$mpas == "Western/Emerald Banks Conservation Area (Restricted Fisheries Zone)") {
csas_keep <- c(csas_keep, which(grepl("Emerald Banks", csas$title, ignore.case=TRUE)))
} else if (state$mpas ==  "St. Anns Bank Marine Protected Area") {
  csas_keep <- c(csas_keep, which(grepl("Anns", csas$title, ignore.case=TRUE)))
}

if (length(csas_keep) > 0) {
  CSAS <- csas[csas_keep,]
  names(CSAS) <- c("Title", "Date")
  print(knitr::kable(CSAS, caption = paste0("CSAS Processes for " , state$mpas),row.names=FALSE))
} else {
  cat("There have been no identified relevant CSAS meetings in the CSAS DMapps related to this area.")
}




```

