---
title: "Annual Report"
output: html_document
---

## Conservation Area

`r params$mpas`

## At-a-glance

```{r, echo=FALSE,comment=NA, results="asis"}
string <- state$mpas
if (!(length(Context[[string]]) == 0)) {
cat(Context[[string]])
} else {
  cat("There is no available context for this area.")
}
```


```{r, echo=FALSE, comment=NA, results="asis"}
cat("<div style='display: flex; gap: 10px;'>")
PALETTE <- append(flowerPalette,list("NA" = "#EDEDED"))
for (name in names(PALETTE)) {
  color <- PALETTE[name]
  cat(sprintf("<div style='width: 50px; height: 20px; background-color: %s; text-align: center; 
               color: black; border: 1px solid #000; line-height: 20px;'>%s</div>", 
               color, name))
}
cat("</div>")
```

## Network Conservation Objectives

```{r, echo=FALSE, comment=NA, results="asis"}
filtered_odf <- odf[odf$objectives %in% N_Objectives, ]

for (fo in seq_along(filtered_odf$objectives)) {
  id <- fo
  req(input$mpas %in% c("Scotian Shelf", unique(pillar_ecol_df$areaID)))
  if (state$mpas == "Scotian Shelf") {
    c1 <- 1:length(pillar_ecol_df$areaID)
  } else {
    c1 <- which(pillar_ecol_df$areaID == state$mpas)
  }
 c2 <- which(tolower(pillar_ecol_df$bin) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
  KEEP <- intersect(c1,c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  if (length(ymax) == 0) {
  # This means it's a ecological objective (i.e. biodiversity, productivity, habitat)
  c2 <- which(tolower(pillar_ecol_df$objective) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
  KEEP <- intersect(c1,c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  }

  #ymax <- ymax[-which(ymax == 0)]
  ymax <- weighted.mean(ymax, weight, na.rm=TRUE)
  # Create data frame for plotting
  data <- data.frame(x = paste0("Objective ", id), y = ymax)
  clc <- as.character(calc_letter_grade(data$y))
  finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
  if (length(finalCol) == 0) {
    finalCol <- "black"
  }
cat(sprintf('<span style="color:%s; background-color:lightgray; padding:3px;"><b>%s</b></span><br>', finalCol, N_Objectives[fo]))
}
```

## Site Conservation Objectives

```{r, echo=FALSE,comment=NA, results="asis"}
string <- input$mpas
keepO <- string


S_Objectives <- Objectives_processed[[keepO]]

if (!(length(S_Objectives) == 0)) {
filtered_odfS <- odf[odf$objectives %in% S_Objectives, ]

for (fo in seq_along(filtered_odfS$objectives)) {
  id <- fo
  req(input$mpas %in% c("All", unique(pillar_ecol_df$areaID)))
  if (state$mpas == "All") {
    c1 <- 1:length(pillar_ecol_df$areaID)
  } else {
    c1 <- which(pillar_ecol_df$areaID == state$mpas)
  }
  
   if (tolower(odf$flower_plot[which(odf$objectives == S_Objectives[id])]) == "environmental (representativity)") {
 c2 <- which(tolower(pillar_ecol_df$bin) == "environmental representativity")

} else {
c2 <- which(tolower(pillar_ecol_df$bin) == tolower(odf$flower_plot[which(odf$objectives == S_Objectives[id])]))
 }
  
  
  KEEP <- intersect(c1, c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  
  # Handling empty or multiple ymax cases
  if (length(ymax) == 0) {
    # This means it's a ecological objective (i.e. biodiversity, productivity, habitat)
    c2 <- which(tolower(pillar_ecol_df$objective) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
    KEEP <- intersect(c1, c2)
    ymax <- pillar_ecol_df$score[KEEP]
    weight <- pillar_ecol_df$weight[KEEP]
  }
  ymax <- weighted.mean(ymax, weight, na.rm = TRUE)
  # Create data frame for plotting
  data <- data.frame(x = paste0("Objective ", id), y = ymax)
  clc <- as.character(calc_letter_grade(data$y))
  finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
  if (length(finalCol) == 0) {
    finalCol <- "black"
  }
cat(sprintf('<span style="color:%s; background-color:lightgray; padding:3px;"><b>%s</b></span><br>', finalCol, S_Objectives[fo]))
}
} else {
  cat("There are no site objectives pulled with our tools for this area.")
}
```


```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
p <- pillar_ecol_df[which(pillar_ecol_df$areaID == string),]
area_grade <- calc_letter_grade(weighted.mean(p$score, p$weight, na.rm=TRUE))

```

```{r, echo=FALSE}
if (string %in% MPA_report_card$NAME_E) {
map <- leaflet() %>%
  addTiles() %>%
  addPolygons(data=MPAs$geoms[which(MPAs$NAME_E == state$mpas)], fillOpacity = 0.5, weight = 2, color=ifelse(is.na(MPA_report_card$grade[which(MPA_report_card$NAME_E == state$mpas)]),"#EDEDED",                                                                                                       flowerPalette[[MPA_report_card$grade[which(MPA_report_card$NAME_E == state$mpas)]]]))
} else {
  map <- leaflet() %>%
  addTiles() %>%
  addPolygons(data=MPAs$geoms[which(MPAs$NAME_E == state$mpas)], fillOpacity = 0.5, weight = 2, color=flowerPalette[[area_grade]])
  
}

map
```

## Creature Feature

FIXME - Get from PPT Milestones/Deliverable

## Research and Monitoring

### CSAS and Publications

FIXME: CSAS From CSAS app/ CSAS website/ PPT
FIXME: Publications from milestones/deliverables


### Flower Plot

```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
plot_flowerplot(pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas),],
                                            grouping = "objective",
                                            labels = "bin",
                                            score = "score",
                                            max_score=100,
                                            min_score=0,
                                            title="Flower plot frame work")
```


As shown above, in `r params$mpas` the over all grade based on our criteria is `r area_grade` with each bin having the following grade:

```{r, echo=FALSE, comment=NA, results="asis"}
for (i in seq_along(unique(p$bin))) {
  keep <- which(p$bin == unique(p$bin)[i])
  df <- p[keep,]
  cat(sprintf("Indicator bin: %s (%s).\n\n", unique(p$bin)[i], calc_letter_grade(weighted.mean(df$score, df$weight,na.rm=TRUE))))
  #cat(sprintf("%s.\n\n", " "))
}
```


```{r, echo=FALSE, comment=NA, results="asis"}
library(knitr)
library(leaflet)

image_folder <- file.path(Sys.getenv("OneDriveCommercial"),
                                    "MarConsNetTargets","data",
                                    "plots")
image_files <- list.files(image_folder, full.names = TRUE)

keeper <- pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas), ]

BINS <- unique(trimws(tolower(unlist(
  strsplit(keeper$bin, ";")
)), "both"))

keeper2 <- NULL

for (i in seq_along(BINS)) {
  KK <- keeper[which(grepl(BINS[i], trimws(tolower(
    keeper$bin
  ), "both"))), ]

  keeper2[[i]] <- data.frame(
    Indicator = KK$indicator,
    Status = KK$status_statement,
    Trend = KK$trend_statement,
    #Plot = KK$plot,
    Grade = KK$score,
    Project = KK$PPTID,
    stringsAsFactors = FALSE
  )
  
}

names(keeper2) <- BINS

for (i in seq_along(keeper2)) {
  cat(sprintf("### Indicator Bin: %s\n\n", BINS[i]))
  for (j in seq_along(keeper2[[i]]$Indicator)) {
    cat(sprintf("<b>Indicator: %s.</b>\n\n", keeper2[[i]]$Indicator[j]))
    
    
    # FINDING PLOT
      k1 <- which(grepl(make.names(state$mpas), image_files, ignore.case=TRUE)) # Which are from the correct area
      k2 <- which(grepl(make.names(keeper2[[i]]$Indicator[j]), image_files, ignore.case=TRUE)) # Which ones have the correct indicator name
      KEEP <- intersect(k1,k2)
      plot_file <- image_files[KEEP]
    
    # END PLOT
      if (length(plot_file) > 0) {
      for (p in seq_along(plot_file)) {
        #cat("![](", plot_file[p], ")\n\n", sep = "")
         cat('<img src="', plot_file[p], '" width="600"/>\n\n', sep = "")
      }
      }
      
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf("%s.\n\n", keeper2[[i]]$Status[j]))
      cat(sprintf("%s.\n\n", keeper2[[i]]$Trend[j]))
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf("This indicator has a score of: %s.\n\n", keeper2[[i]]$Grade[j]))
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf(
        "Data was provided from project %s.\n\n",
        keeper2[[i]]$Project[j]
      ))
  }
}

```

## Discussion

FIXME: Useful to get groupings of indicators here

## Collaborations and partnerships

FIXME: Get from PPT



