---
title: "Generated Report"
output: html_document
---

# Introduction

### Conservation Area

`r params$mpas`

```{r, echo=FALSE, comment=NA, results="asis"}
cat("<div style='display: flex; gap: 10px;'>")
for (name in names(flowerPalette)) {
  color <- flowerPalette[name]
  cat(sprintf("<div style='width: 50px; height: 20px; background-color: %s; text-align: center; 
               color: black; border: 1px solid #000; line-height: 20px;'>%s</div>", 
               color, name))
}
cat("</div>")
```

### Network Objectives
```{r, echo=FALSE, comment=NA, results="asis"}
string <- state$mpas

filtered_odf <- odf[odf$objectives %in% N_Objectives, ]

for (fo in seq_along(filtered_odf$objectives)) {
  id <- fo
  req(input$mpas %in% c("Scotian Shelf", unique(pillar_ecol_df$areaID)))
  if (state$mpas == "Scotian Shelf") {
    c1 <- 1:length(pillar_ecol_df$areaID)
  } else {
    c1 <- which(pillar_ecol_df$areaID == state$mpas)
  }
 c2 <- which(tolower(pillar_ecol_df$bin) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
  KEEP <- intersect(c1,c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  if (length(ymax) == 0) {
  # This means it's a ecological objective (i.e. biodiversity, productivity, habitat)
  c2 <- which(tolower(pillar_ecol_df$objective) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
  KEEP <- intersect(c1,c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  }

  #ymax <- ymax[-which(ymax == 0)]
  ymax <- weighted.mean(ymax, weight, na.rm=TRUE)
  # Create data frame for plotting
  data <- data.frame(x = paste0("Objective ", id), y = ymax)
  clc <- as.character(calc_letter_grade(data$y))
  finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
  if (length(finalCol) == 0) {
    finalCol <- "black"
  }
cat(sprintf('<span style="color:%s; background-color:lightgray; padding:3px;"><b>%s</b></span><br>', finalCol, N_Objectives[fo]))
}
```

### Site Objectives

```{r, echo=FALSE,comment=NA, results="asis"}
string <- input$mpas
keepO <- string


S_Objectives <- Objectives_processed[[keepO]]


filtered_odfS <- odf[odf$objectives %in% S_Objectives, ]

for (fo in seq_along(filtered_odfS$objectives)) {
  id <- fo
  req(input$mpas %in% c("All", unique(pillar_ecol_df$areaID)))
  if (state$mpas == "All") {
    c1 <- 1:length(pillar_ecol_df$areaID)
  } else {
    c1 <- which(pillar_ecol_df$areaID == state$mpas)
  }
  
   if (tolower(odf$flower_plot[which(odf$objectives == S_Objectives[id])]) == "environmental (representativity)") {
 c2 <- which(tolower(pillar_ecol_df$bin) == "environmental representativity")

} else {
c2 <- which(tolower(pillar_ecol_df$bin) == tolower(odf$flower_plot[which(odf$objectives == S_Objectives[id])]))
 }
  
  
  KEEP <- intersect(c1, c2)
  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  
  # Handling empty or multiple ymax cases
  if (length(ymax) == 0) {
    # This means it's a ecological objective (i.e. biodiversity, productivity, habitat)
    c2 <- which(tolower(pillar_ecol_df$objective) == tolower(odf$flower_plot[which(odf$objectives == N_Objectives[id])]))
    KEEP <- intersect(c1, c2)
    ymax <- pillar_ecol_df$score[KEEP]
    weight <- pillar_ecol_df$weight[KEEP]
  }
  ymax <- weighted.mean(ymax, weight, na.rm = TRUE)
  # Create data frame for plotting
  data <- data.frame(x = paste0("Objective ", id), y = ymax)
  clc <- as.character(calc_letter_grade(data$y))
  finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
  if (length(finalCol) == 0) {
    finalCol <- "black"
  }
cat(sprintf('<span style="color:%s; background-color:lightgray; padding:3px;"><b>%s</b></span><br>', finalCol, S_Objectives[fo]))
}
```


### Context

```{r, echo=FALSE,comment=NA, results="asis"}
cat(Context[[string]])
```


```{r, echo=FALSE}
map <- leaflet() %>%
  addTiles() %>%
  addPolygons(data=MPAs$geoms[which(MPAs$NAME_E == state$mpas)], fillOpacity = 0.5, weight = 2, color=flowerPalette[[MPA_report_card$grade[which(MPA_report_card$NAME_E == string)]]])

map
```


# Methods

The status of `r params$mpas` is reported using the flower plot frame work, shown below in Figure 1. This approach provides a mechanism to bin indicators into bins: Genetic Diversity, Species Diversity, Functional Diversity, Environmental Representativity, Key Fish Habitat,               Connectivity, Uniqueness, Threats to Habitat, Biomass Metrics, Structure and Function, and Threats to Productivity. It then provides a means to report on the status of each bin in different protected/conserved areas even though we do not have measurements of the same indicators in all areas.

The score is calculated by determining the desired trend of the indicator, then
looking at the actual trend of the indicator. If the trend

- is statistically significant AND matches the desired direction for the
indicator, a score of A is assigned.
- is not statistically significant but matches the desired direction for
the indicator, a B is assigned
- Has no change a C is assigned
- is not statistically significant and going is the opposite direction
of the desired direction a D is assigned
- is statistically significant and going in the opposite direction,
a F is assigned.

For each bin (and area of interest), the weighted mean is taken to determine the overall score.


# Results

### Flower plot

```{r, echo=FALSE, comment=NA, results="asis", warn=FALSE}
plot_flowerplot(pillar_ecol_df[which(pillar_ecol_df$areaID == input$mpas),],
                                            grouping = "objective",
                                            labels = "bin",
                                            score = "score",
                                            max_score=100,
                                            min_score=0,
                                            title="Flower plot frame work")
```



```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
p <- pillar_ecol_df[which(pillar_ecol_df$areaID == string),]
area_grade <- calc_letter_grade(weighted.mean(p$score, p$weight, na.rm=TRUE))

```

As shown above, in `r params$mpas` the over all grade based on our criteria is `r area_grade` with each bin having the following grade:

```{r, echo=FALSE, comment=NA, results="asis"}
for (i in seq_along(unique(pillar_ecol_df$bin))) {
  keep <- which(pillar_ecol_df$bin == unique(pillar_ecol_df$bin)[i])
  df <- pillar_ecol_df[keep,]
  cat(sprintf("Indicator bin: %s (%s).\n\n", unique(pillar_ecol_df$bin)[i], calc_letter_grade(weighted.mean(df$score, df$weight,na.rm=TRUE))))
  #cat(sprintf("%s.\n\n", " "))
      }
```


```{r, echo=FALSE, comment=NA, results="asis"}
library(knitr)
library(leaflet)

image_folder <- file.path(Sys.getenv("OneDriveCommercial"),
                                    "MarConsNetTargets","data",
                                    "plots")
image_files <- list.files(image_folder, full.names = TRUE)

keeper <- pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas), ]

BINS <- unique(trimws(tolower(unlist(
  strsplit(keeper$bin, ";")
)), "both"))

keeper2 <- NULL

for (i in seq_along(BINS)) {
  KK <- keeper[which(grepl(BINS[i], trimws(tolower(
    keeper$bin
  ), "both"))), ]

  keeper2[[i]] <- data.frame(
    Indicator = KK$indicator,
    Status = KK$status_statement,
    Trend = KK$trend_statement,
    #Plot = KK$plot,
    Grade = KK$score,
    Project = KK$PPTID,
    stringsAsFactors = FALSE
  )
  
}

names(keeper2) <- BINS

for (i in seq_along(keeper2)) {
  cat(sprintf("### Indicator Bin: %s\n\n", BINS[i]))
  for (j in seq_along(keeper2[[i]]$Indicator)) {
    cat(sprintf("<b>Indicator: %s.</b>\n\n", keeper2[[i]]$Indicator[j]))
    
    
    # FINDING PLOT
      k1 <- which(grepl(make.names(state$mpas), image_files, ignore.case=TRUE)) # Which are from the correct area
      k2 <- which(grepl(make.names(keeper2[[i]]$Indicator[j]), image_files, ignore.case=TRUE)) # Which ones have the correct indicator name
      KEEP <- intersect(k1,k2)
      plot_file <- image_files[KEEP]
    
    # END PLOT
      if (length(plot_file) > 0) {
      for (p in seq_along(plot_file)) {
        cat("![](", plot_file[p], ")\n\n", sep = "")
      }
      }
      
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf("%s.\n\n", keeper2[[i]]$Status[j]))
      cat(sprintf("%s.\n\n", keeper2[[i]]$Trend[j]))
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf("This indicator has a score of: %s.\n\n", keeper2[[i]]$Grade[j]))
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf(
        "Data was provided from project %s.\n\n",
        keeper2[[i]]$Project[j]
      ))
  }
}

```

# Discussion

### Climate Change

The following indicators have been identified as direct measure of climate change and are measured in `r params$mpas`:


```{r, echo=FALSE, comment=NA, results="asis"}
# trends <- pillar_ecol_df$trend_statement[which(tolower(pillar_ecol_df$indicator) %in% tolower(climate_change$indicators))]
# analysis <- NULL
# for (i in seq_along(trends)) {
#   if (!(grepl("BLANK", trends[i]))) {
#   analysis[[i]] <- climate_analysis(trend=trends[i], itp=indicator_to_plot)
#   } else {
#   analysis[[i]] <- "There is no data for this indicator yet."
#   }
# }
# 
# 
# for (i in seq_along(climate_change$indicators)) {
#       cat(sprintf("<b>Indicator: %s.</b>\n\n", climate_change$indicators[i]))
#       cat(sprintf("%s.\n\n", " "))
#       cat(sprintf("%s.\n\n", climate_change$summary[i]))
#       cat(sprintf("%s.\n\n", " "))
#       cat(sprintf("Actual results showed:\n\n"))
#       cat(sprintf("%s.\n\n", analysis[[i]]))
# }
```





