---
title: "Annual Report"
output: 
html_document:
  self_contained: false
---

## Conservation Area

`r params$mpas`


## Key Findings

```{r, echo=FALSE}
library(sf)
library(leaflet)
library(rgbif)
library(rvest)
library(dplyr)
library(DT)

## PREP FOR KEY FINDINGS

# AREA GRADE
last_year <- paste0((as.numeric(format(Sys.time(), "%Y"))-1),"-", format(Sys.time(), "%Y"))
string <- state$mpas
p <- pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas),]
area_grade <- calc_letter_grade(weighted.mean(p$score, p$weight, na.rm=TRUE))

## SUGGESTED FURTHER RESEARCH

summary_table <- data.frame(
  `Indicator Bin` = character(),
  `Grade` = character(),
  `Number of Indicators` = character(),
  stringsAsFactors = FALSE
)

# Loop through bins and calculate grades
for (i in seq_along(unique(p$bin))) {
  keep <- which(p$bin == unique(p$bin)[i])
  df <- p[keep, ]
  
  grade <- calc_letter_grade(weighted.mean(df$score, df$weight, na.rm = TRUE))
  
  if (any(is.na(df$indicator) | df$indicator == "placeholder" | is.na(df$score))) {
  indicatorLength <- length(df$indicator[-which(is.na(df$indicator) | df$indicator == "placeholder" | is.na(df$score))])
  } else {
    indicatorLength <- length(df$indicator)
  }
  
  summary_table[i, ] <- c(unique(p$bin)[i], grade, indicatorLength)
}

# PERCENT FUNDING FOR THIS AREA
com <- cost_of_mpas[which(cost_of_mpas$area == state$mpas & !(round(cost_of_mpas$percent_sites_in_mpa,0) == 0)),]

if (length(com$project_id) != 0) {
proj_titles <- sapply(com$project_id, function(pid) {
    unique(pillar_ecol_df$project_short_title[which(pillar_ecol_df$PPTID == pid)])
})
proj <- unique(com$project_id)

# PERCENT FUNDING
pie_area <- unique(cost_of_mpas$area)
ps <- split(cost_of_mpas, cost_of_mpas$area)

adjusted_ps <- list()
for (i in seq_along(ps)) {
  PS <- ps[[i]]
  adjusted_ps[[i]] <- data.frame(
    project_id = PS$project_id,
    amount = rep(NA, length(PS$project_id))
  )
  for (j in seq_along(PS$project_id)) {
    keep <- which(om$project_id == PS$project_id[j])
    adjusted_ps[[i]]$amount[j] <- sum(om$amount[keep] * PS$percent_sites_in_mpa[j])
  }
}

final_funding <- lapply(adjusted_ps, function(x) sum(x$amount))

names(final_funding) <- names(ps)

bad <- which(unname(final_funding) == 0)

percent_funding <- data.frame( #old df
  MPA = names(final_funding)[-bad],
  Funding = unname(unlist(final_funding))[-bad]
) %>%
  mutate(Funding_pct = Funding / sum(Funding))

money_percentage <- round(percent_funding$Funding_pct[which(percent_funding$MPA == state$mpas)]*100, 2)

investment <- paste0("The following DFO projects have sampled in ",
             state$mpas, " : ",
             paste0(paste(proj, " (", proj_titles, ")", sep = ""), collapse="; "), " which accounted for ", money_percentage, "% of O&M funding to the protected areas.")
} else {
  investment <- paste0("No identified DFO projects have sampled in ", state$mpas, " and therefore there is no identified O&M investment.")
}

# STATUS OF OBJECTIVES

string <- state$mpas
keepO <- string

# Get site-level objectives
S_Objectives <- Objectives_processed[[keepO]]

# Initialize the table
objective_table_site <- data.frame(
  Objective = character(),
  Flower_Plot_Linkage = character(),
  Rationale = character(),
  stringsAsFactors = FALSE
)


if (!(length(S_Objectives) == 0)) {
  filtered_odfS <- odf[odf$objectives %in% S_Objectives, ]

  objectives_letter_grades <- NULL

  for (fo in seq_along(filtered_odfS$objectives)) {
    id <- fo
    req(input$mpas %in% c("All", unique(pillar_ecol_df$areaID)))

    # Subset rows by MPA
    if (state$mpas == "All") {
      c1 <- 1:length(pillar_ecol_df$areaID)
    } else {
      c1 <- which(pillar_ecol_df$areaID == state$mpas)
    }

    # Get flower plot linkage name
    flower_linkage_name <- odf$flower_plot[which(odf$objectives == S_Objectives[id])]

    # Special handling for environmental representativity
    if (tolower(flower_linkage_name) == "environmental (representativity)") {
      c2 <- which(tolower(pillar_ecol_df$bin) == "environmental representativity")
    } else {
      c2 <- which(tolower(pillar_ecol_df$bin) == tolower(flower_linkage_name))
    }

    KEEP <- intersect(c1, c2)
    ymax <- pillar_ecol_df$score[KEEP]
    weight <- pillar_ecol_df$weight[KEEP]

    # Fallback match by 'objective' field
    if (length(ymax) == 0) {
      c2 <- which(tolower(pillar_ecol_df$objective) == tolower(flower_linkage_name))
      KEEP <- intersect(c1, c2)
      ymax <- pillar_ecol_df$score[KEEP]
      weight <- pillar_ecol_df$weight[KEEP]
    }

    # Calculate weighted mean
    ymax <- weighted.mean(ymax, weight, na.rm = TRUE)

    # Convert score to grade → color
    clc <- as.character(calc_letter_grade(ymax))
    objectives_letter_grades[id] <- clc
    finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
    if (length(finalCol) == 0) finalCol <- "#EDEDED"

    # Add row to site-level table with HTML color styling
    objective_table_site <- rbind(objective_table_site, data.frame(
      Objective = sprintf(
        '<span style="color:%s; padding:3px; text-shadow: -1px -1px 0 black, 1px -1px 0 black, -1px 1px 0 black, 1px 1px 0 black;"><b>%s</b></span>',
        finalCol, S_Objectives[fo]
      ),
      Flower_Plot_Linkage = flower_linkage_name,
      Rationale = NA_character_,
      stringsAsFactors = FALSE
    ))
  }

  status_objectives <- HTML(paste0(
  "Based on our analysis, the status of the objectives are as follows:<br><br>",
  paste0(
    paste(gsub("\n", "", filtered_odfS$objectives),
          " (", objectives_letter_grades, ")", sep = ""),
    collapse = "<br><br>"
  )
))
} else {
  status_objectives <- "No site objective status available."
}

div(
  style = "border: 2px solid black; padding: 10px; border-radius: 5px; background-color: #f9f9f9;",
  tags$p(investment),
  tags$p(paste0(state$mpas, " has an overall status score of ", area_grade, ".")),
  tags$p(status_objectives),
  tags$p(paste0(
    "No data exists for the following indicators bins: ",
    paste0(summary_table$Indicator.Bin[which(summary_table$Grade == "NA")], collapse = ", "),
    ". Further research is recommended."
  ))
)


```




## At-a-glance

```{r, echo=FALSE,comment=NA, results="asis"}
if (!(length(Context[[string]]) == 0)) {
cat(Context[[string]])
} else {
  cat("There is no available context for this area.")
}
```


```{r, echo=FALSE, comment=NA, results="asis"}
cat("<div style='display: flex; gap: 10px;'>")
PALETTE <- append(flowerPalette,list("NA" = "#EDEDED"))
for (name in names(PALETTE)) {
  color <- PALETTE[name]
  cat(sprintf("<div style='width: 50px; height: 20px; background-color: %s; text-align: center; 
               color: black; border: 1px solid #000; line-height: 20px;'>%s</div>", 
               color, name))
}
cat("</div>")
```

## Network Conservation Objectives

```{r, echo=FALSE, comment=NA, results="asis"}
# Initialize empty list of colored objectives
colored_objectives <- c()

filtered_odf <- odf[odf$objectives %in% N_Objectives, ]

for (fo in seq_along(filtered_odf$objectives)) {
  id <- fo
  req(input$mpas %in% c("Scotian Shelf", unique(pillar_ecol_df$areaID)))

  if (state$mpas == "Scotian Shelf") {
    c1 <- 1:length(pillar_ecol_df$areaID)
  } else {
    c1 <- which(pillar_ecol_df$areaID == state$mpas)
  }

  flower_linkage_name <- odf$flower_plot[which(odf$objectives == N_Objectives[id])]

  # Try to match by bin
  c2 <- which(tolower(pillar_ecol_df$bin) == tolower(flower_linkage_name))
  KEEP <- intersect(c1, c2)

  # Fallback: match by objective
  if (length(KEEP) == 0) {
    c2 <- which(tolower(pillar_ecol_df$objective) == tolower(flower_linkage_name))
    KEEP <- intersect(c1, c2)
  }

  ymax <- pillar_ecol_df$score[KEEP]
  weight <- pillar_ecol_df$weight[KEEP]
  ymax <- weighted.mean(ymax, weight, na.rm = TRUE)

  # Convert score to grade + color
  clc <- as.character(calc_letter_grade(ymax))
  finalCol <- unname(flowerPalette[which(names(flowerPalette) == clc)])
  if (length(finalCol) == 0) finalCol <- "#EDEDED"

  # Store styled objective label
  colored_objectives <- c(
    colored_objectives,
    sprintf(
      '<span style="color:%s; padding:3px; text-shadow: -1px -1px 0 black, 1px -1px 0 black, -1px 1px 0 black, 1px 1px 0 black;"><b>%s</b></span>',
      finalCol, N_Objectives[fo]
    )
  )
}

# Display just the objectives (HTML-rendered in Shiny/RMarkdown)
HTML(paste(colored_objectives, collapse = "<br>"))



```

## Site Conservation Objectives

```{r, echo=FALSE,comment=NA, results="asis"}

if (!(length(S_Objectives) == 0)) {
  
  
  site_objectives <- HTML(paste0(
  "Based on our analysis, the status of the objectives are as follows:<br><br>",
  paste0(
    paste(objective_table_site$Objective, sep = ""),
    collapse = "<br><br>"
  )
))

  site_objectives
  
  
} else {
  cat("There are no site objectives pulled with our tools for this area.")
}



```


```{r, echo=FALSE,message=FALSE, warning=FALSE}
library(htmltools)
if (state$mpas %in% MPA_report_card$NAME_E) {
  fill_color <- ifelse(
    is.na(MPA_report_card$grade[which(MPA_report_card$NAME_E == state$mpas)]),
    "#EDEDED",
    flowerPalette[[MPA_report_card$grade[which(MPA_report_card$NAME_E == state$mpas)]]]
  )

  # Set border color conditionally
  border_color <- if (fill_color == "#ABD9E9") "black" else fill_color

} else {
  fill_color <- flowerPalette[[area_grade]]
  border_color <- if (fill_color == "#ABD9E9") "black" else fill_color
}
 ggplot(MPAs$geoms[which(MPAs$NAME_E == state$mpas)]) +
  geom_sf(fill = fill_color, color = border_color) +
  theme_minimal()


```

## Creature Feature

```{r, echo = FALSE, comment=NA, results="asis", warning=FALSE}
try({
  inatoccs <- occ_search(geometry = st_as_text(st_as_sfc(st_bbox(MPAs[MPAs$NAME_E == state$mpas,]))),institutionCode = "iNaturalist",limit = 100000)
  
  sptable <-  inatoccs$data |> 
    st_as_sf(
      coords = c("decimalLongitude", "decimalLatitude"),
      crs = 4326,
      remove = FALSE
    ) |> 
    st_filter(MPAs[MPAs$NAME_E == state$mpas,]) |>
    as.data.frame() |> 
    filter(!is.na(speciesKey),
           kingdom != "Plantae"|genus == "Zostera", # remove plants except eelgrass
           class!="Mammalia"|family %in% c("Phocidae","Otarioidea"), #remove mammals except seals
           class!="Reptilia"|family %in% c("Cheloniidae","Dermochelyidae"),# remove reptiles except sea turtles
           phylum!="Basidiomycota",phylum!="Ascomycota") |> # remove mushrooms and lichens
    group_by(speciesKey,scientificName,kingdom, phylum, class) |>
    reframe(n=n(),
            exampleurl = references[1],
            rightsHolder = rightsHolder[1]) |> 
    arrange(desc(n)) |>
    # head(10) |>
    rowwise() |>
    mutate(commonname = NA,
           imageurl = {
             url <- try(read_html(exampleurl) |>
                          html_node('meta[property="og:image"]') |> 
                          html_attr('content'))
             if (inherits(url, "try-error")) {
               NA
             } else {
               url
             }
           },
           image_column = paste0(
             '<a href="', exampleurl, '" target="_blank">',
             '<img src="', imageurl, '" style="max-height: 100px; max-width: 100px; object-fit: cover;"/>',
             '<br>',rightsHolder,'</br>',
             '</a>'
           )) 
  
  for(i in 1:nrow(sptable)){
    spnames <- try(name_usage(sptable$speciesKey[i], data = "vernacularNames")[[2]] )
    if(nrow(spnames)>0|| !inherits(spnames, "try-error")) {
      cn <- spnames |>
        as.data.frame() |>
        filter(language == "eng") |> 
        pull(vernacularName) |>
        table() |> 
        sort(decreasing = TRUE) |>
        head(1) |> 
        names()
      if(!is.null(cn)){
        sptable$commonname[i] <- cn
      }
    }
  }
  
  datatable(
    sptable |> 
      dplyr::select(commonname, image_column, scientificName, n, kingdom, phylum, class),
    
    # Disable sorting for the image column
    options = list(
      # Show 5 entries by default
      pageLength = 5,
      
      # Enable column-specific filtering
      initComplete = JS(
        "function(settings, json) {
          this.api().columns([1, 3, 4, 5, 6, 7]).every(function() {
            var column = this;
            var select = $('<select><option value=\"\"></option></select>')
              .appendTo($(column.footer()).empty())
              .on('change', function() {
                var val = $.fn.dataTable.util.escapeRegex(
                  $(this).val()
                );

                column
                  .search(val ? '^' + val + '$' : '', true, false)
                  .draw();
              });

            column.data().unique().sort().each(function(d, j) {
              select.append('<option value=\"' + d + '\">' + d + '</option>')
            });
          });
        }"
      )
    ),
    
    # Specify column names
    colnames = c(
      "Common Name",
      "Example Image",
      "Scientific Name", 
      "iNaturalist Observations",
      "Kingdom",
      "Phylum",
      "Class"
    ),
    
    # Escape HTML to allow image rendering
    escape = FALSE,
    
    # Add some styling
    class = 'cell-border stripe hover',
    
    # Add footer for filtering
    filter = "bottom"
  )
})
```



## Research and Monitoring

### Flower Plot

```{r, echo=FALSE, comment=NA, results="asis", warning=FALSE}
plot_flowerplot(pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas),],
                                            grouping = "objective",
                                            labels = "bin",
                                            score = "score",
                                            max_score=100,
                                            min_score=0,
                                            title="Flower plot frame work")
```


As shown above, in `r params$mpas` the over all grade based on our criteria is `r area_grade` with each bin having the following grade:

```{r, echo=FALSE, comment=NA, results="asis"}
# Create an empty data frame to store results
print(knitr::kable(summary_table, caption = "Grades by Indicator Bin"))


```


```{r, echo=FALSE, comment=NA, results="asis"}
library(knitr)
library(leaflet)

image_folder <- file.path(Sys.getenv("OneDriveCommercial"),
                                    "MarConsNetTargets","data",
                                    "plots")
image_files <- list.files(image_folder, full.names = TRUE)

keeper <- pillar_ecol_df[which(pillar_ecol_df$areaID == state$mpas), ]

BINS <- unique(trimws(tolower(unlist(
  strsplit(keeper$bin, ";")
)), "both"))


keeper2 <- NULL

for (i in seq_along(BINS)) {
  KK <- keeper[which(grepl(BINS[i], trimws(tolower(
    keeper$bin
  ), "both"))), ]
  
  # Remove NA and placeholder indicators
  
  if (any(is.na(KK$indicator) | KK$indicator == "placeholder" | is.na(KK$score))) {
    KK <- KK[-(which(is.na(KK$indicator) | KK$indicator == "placeholder" | is.na(KK$score))),]
  }
  
  keeper2[[i]] <- data.frame(
    Indicator = KK$indicator,
    Status = KK$status_statement,
    Trend = KK$trend_statement,
    #Plot = KK$plot,
    Grade = KK$score,
    Project = KK$PPTID,
    Source = KK$source,
    Rationale=KK$indicator_rationale,
    stringsAsFactors = FALSE
  )
  
}

names(keeper2) <- BINS

for (i in seq_along(keeper2)) {
  cat(sprintf('<details><summary><strong>Indicator Bin: %s</strong></summary>\n\n', toupper(BINS[i])))
  
  if (!(length(keeper2[[i]]$Indicator) == 0)) {
  for (j in seq_along(keeper2[[i]]$Indicator)) {
    cat(sprintf("<b>Indicator: %s.</b>\n\n", keeper2[[i]]$Indicator[j]))
    
    cat(sprintf("%s.\n\n", keeper2[[i]]$Rationale[j]))
    
    
    # FINDING PLOT
      k1 <- which(grepl(make.names(state$mpas), image_files, ignore.case=TRUE)) # Which are from the correct area
      k2 <- which(grepl(make.names(keeper2[[i]]$Indicator[j]), image_files, ignore.case=TRUE)) # Which ones have the correct indicator name
      KEEP <- intersect(k1,k2)
      
      if (length(KEEP) > 1) {
        KEEP <- KEEP[which(sub(".*_(.*?)\\.png$", "\\1", image_files[KEEP]) == keeper2[[i]]$Indicator[j])]
      }
      plot_file <- image_files[KEEP]
    
    # END PLOT
      if (length(plot_file) > 0) {
      for (p in seq_along(plot_file)) {
        #cat("![](", plot_file[p], ")\n\n", sep = "")
         cat('<img src="', plot_file[p], '" width="600"/>\n\n', sep = "")
      }
      }
      
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf("%s.\n\n", keeper2[[i]]$Status[j]))
      if (is.na(keeper2[[i]]$Trend[j])) {
        cat(sprintf("%s.\n\n", "No temporal analysis completed for this indicator."))
      } else if (!(keeper2[[i]]$Trend[j] == "There is no temporal dimension in this data.")) {
      cat(sprintf("%s.\n\n", keeper2[[i]]$Trend[j]))
      }
      cat(sprintf("%s.\n\n", " "))
      cat(sprintf(
  "This indicator has a score of: %s.\n\nBased on the following scoring scheme: %s\n",
  keeper2[[i]]$Grade[j],
  pillar_ecol_df$scoring[
    which(
      pillar_ecol_df$indicator == keeper2[[i]]$Indicator[j] &
      pillar_ecol_df$areaID == state$mpas
    )
  ]
))

      cat(sprintf("%s.\n\n", " "))
      cat(sprintf(
        "Data was provided from %s.\n\n",
        ifelse(is.na(keeper2[[i]]$Project[j]), keeper2[[i]]$Source[j], keeper2[[i]]$Project[j])
      ))
  } # END HERE
  
  } else {
  cat("There are no indicators in the app for this indicator bin.")
}
  cat("</details>\n\n")
}


```

## Investment Information

```{r disclaimer_site, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
if (length(com$project_id) != 0) {
  cat("<p>Disclaimer: The cost information is based on the funding information in the project planning tool. 
      The amount is based on percentage of samples taken in the area of interest.</p>")
  
  
  om_in_site <- om[which(om$project_id %in% unique(com$project_id)),]

  for (i in seq_along(unique(com$project_id))) {
    p_id <- as.numeric(unique(com$project_id)[i])
    percentage <- com$percent_sites_in_mpa[which(com$project_id == p_id)]
    om_in_site$amount[which(om_in_site$project_id == p_id)] <- om_in_site$amount[which(om_in_site$project_id == p_id)] * (percentage/100)
  }
  
} else {
  cat("<p>There is no internal investment information available for this area.</p>")
}
```

```{r,results='asis', message=FALSE, error=FALSE, warning=FALSE, echo=FALSE}
if (length(com$project_id) != 0) {
dataSPA_plot <- dataSPA::plotSPA(om = om_in_site, which = "omBar")


# Save to a temporary HTML file
tmp_html <- tempfile(fileext = ".html")
saveWidget(dataSPA_plot, tmp_html, selfcontained = TRUE)

# Temporary PNG file path
tmp_png <- tempfile(fileext = ".png")

# Take a snapshot of the HTML widget
webshot(tmp_html, file = tmp_png, vwidth = 1000, vheight = 1000)

# Insert into the Rmd as a static image
#include_graphics(tmp_png)

} else {
  NULL
}
```

```{r cost_projects, echo=FALSE, results='asis', message=FALSE, warning=FALSE}

if (length(com$project_id) != 0) {
  cat(paste0("<p>The investment information is based on the following internal DFO projects that have had samples in ",
             state$mpas, " : ",
             paste0(paste(proj, " (", proj_titles, ")", sep = ""), collapse="; "),
             "</p>"))
}
```


```{r money_map, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
apg <- all_project_geoms[-which(is.na(all_project_geoms$PPTID)),]
if (any(apg$areaID == "Non_Conservation_Area")) {
  apg <- apg[-which(apg$areaID == "Non_Conservation_Area"),]
}
# Create a new geometry list with rounded coords
rounded_geoms <- st_sfc(
  lapply(st_geometry(apg), function(pt) {
    coords <- st_coordinates(pt)
    coords_rounded <- round(coords, 2)
    coords_vec <- as.numeric(coords_rounded[1, ])
    st_point(coords_vec)
  }),
  crs = st_crs(apg)
)

# Then assign back to the sf object properly
st_geometry(apg) <- rounded_geoms

# Now find unique geometries
apg_unique <- apg %>% distinct(geometry, .keep_all = TRUE)

# Getting lat and lng
coords_df <- do.call(rbind, lapply(st_geometry(apg_unique), function(pt) {
  c(lng = pt[1], lat = pt[2])
}))

# Add as columns to apg
apg_unique <- apg_unique %>%
  mutate(
    lng = coords_df[, "lng"],
    lat = coords_df[, "lat"]
  )

# Getting colors for polygons

money_mpas <- MPAs[which(MPAs$NAME_E %in% state$mpas),]

# GETTING PROJECTS
pptids <- unique(apg_unique$PPTID)

marker_color <- "lightblue"

# Assign FA icons for shapes
shape_icons <- c("anchor", "ship", "circle", "life-ring", "sailboat", "map-marker", "globe", "compass", "flag", "cloud", "water", "tint", "wave-square", "sun-o", "moon-o", "star", "bolt", "paper-plane", "location-arrow", "road", "truck", "ship-wheel", "life-ring", "circle", "square", "circle-o", "square-o", "dot-circle-o")


# Legend work
shape_map <- setNames(rep(shape_icons, length.out = length(pptids)), pptids)

# Set icons
apg_unique$map_icons <- NA
for (i in seq_along(pptids)) {
  apg_unique$map_icons[which(apg_unique$PPTID == as.numeric(pptids[i]))] <- shape_map[[which(names(shape_map) == pptids[i])]]
}

icons <- awesomeIcons(
  icon = apg_unique$map_icons,
  iconColor = "black",
  library = "fa",
  markerColor = marker_color
)

# Build legend items dynamically:
legend_items <- paste0(
  "<i class='fa fa-", shape_map[pptids], "' style='color: ", marker_color, ";'></i> ", pptids
)

# Combine into one HTML string
legend_html <- paste0(
  "<div style='background: white; padding: 8px; font-family: Arial;'>",
  "<b>Legend</b><br>",
  paste(legend_items, collapse = "<br>"),
  "</div>"
)


map <- leaflet(apg_unique[which(apg_unique$areaID == state$mpas),]) %>%
    addTiles() %>%
    addPolygons(
        data = money_mpas$geoms,
        fillColor = ifelse(money_mpas$NAME_E == state$mpas, fill_color, "lightgray"),
        fillOpacity = 0.9,
        color = "grey30",
        weight = 6,
        opacity = 1
    )%>%
  addAwesomeMarkers(
    ~lng, ~lat,
    icon = icons,
    popup = ~paste("Project ID:", PPTID)
  )%>%
  addControl(
    html = legend_html,
    position = "bottomright"
  )


# Saving the map as stagnant
tmp_html <- tempfile(fileext = ".html")
saveWidget(map, tmp_html, selfcontained = TRUE)

# Temporary PNG file path
tmp_png <- tempfile(fileext = ".png")

# Take a snapshot of the HTML widget
#webshot(tmp_html, file = tmp_png, vwidth = 1000, vheight = 1000,quiet=TRUE)



# ggplot pie chart
percent_funding <- percent_funding %>%
  mutate(
    fill_col = ifelse(MPA == state$mpas, fill_color, "gray"),
    legend_label = ifelse(MPA == state$mpas, MPA, "Other Protected Areas")  # ⬅ RED DOT: legend_label matches what we want in the legend
  )

# Named vector for scale_fill_manual
fill_values <- setNames(
  c(fill_color, "gray"),
  c(state$mpas, "Other Protected Areas")  # ⬅ RED DOT: name matches legend_label exactly
)

# Plot
gg_pie <- ggplot(percent_funding, aes(x = "", y = Funding_pct, fill = legend_label)) +
  geom_col(width = 1) +
  coord_polar(theta = "y") +
  scale_fill_manual(
    values = fill_values,
    name = "Protected Area"
  ) +
  labs(title = "Percentage of Funding by MPA") +
  theme_void()

#gg_pie
temp_file <- tempfile(fileext = ".png")
ggsave(temp_file, plot = gg_pie, width = 6, height = 4, dpi = 150)

tagList(
  tags$div(style = "display: flex; gap: 20px; align-items: center;",
           # Pie chart
           tags$div(style = "flex: 1;",
                    tags$img(
                      src = base64enc::dataURI(file = temp_file, mime = "image/png"),
                      style = "max-width: 100%; height: auto;"
                    )
           ),
           # Leaflet map snapshot
           tags$div(style = "flex: 1;",
                    tags$img(
                      src = base64enc::dataURI(file = webshot(tmp_html, file = tmp_png, vwidth = 1000, vheight = 1000)
, mime = "image/png"),  # ⬅ RED CHANGE: insert PNG of map
                      style = "max-width: 100%; height: auto;"                      # ⬅ RED CHANGE: style for map image
                    )
           )
  )
)



```


## Discussion

```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}

cat("### Climate Change\n")

climate_indicators <- unique(pillar_ecol_df$indicator[which(grepl("Inside", pillar_ecol_df$indicator) & pillar_ecol_df$areaID == state$mpa)])

for (i in seq_along(climate_indicators)) {
  indicator_keep <- which(pillar_ecol_df$indicator == gsub(" Inside Outside Comparison$", "", climate_indicators[i]) & pillar_ecol_df$areaID == state$mpas)
  
  if (!(length(indicator_keep) == 0) & !(is.na(pillar_ecol_df$trend_statement[indicator_keep]))) {
    
    excel_keep <- which(climate$Indicator == climate_indicators[i])
    pillar_keep_inside <- which(pillar_ecol_df$indicator == climate_indicators[i] & pillar_ecol_df$areaID == state$mpas)
    
    cat(sprintf("<b>Indicator: %s.</b>\n\n",toupper(climate_indicators[i])))
    
    cat(climate$Context[excel_keep], "\n\n")
    cat("In our analysis, ")
    cat(pillar_ecol_df$trend_statement[indicator_keep])
    
    if (!(grepl("There is only one year of data", pillar_ecol_df$trend_statement[indicator_keep]))) {
    
    pval <- str_extract(pillar_ecol_df$trend_statement[indicator_keep], "pval\\s*=\\s*\\d+(\\.\\d+)?") |>
      str_extract("\\d+(\\.\\d+)?") |>
      as.numeric()
    
    if (pval > 0.05) {
      cat(". The change in this indicator in the MPA is not significant.")
    } else {
      cat(". The change in this indicator in the MPA is significant.")
    }
    
    cat(" An inside/outside comparison was done to help understand the impacts of climate change on this variable. Results showed ")
    
    result <- pillar_ecol_df$status_statement[pillar_keep_inside]
    
    cat(paste0(tolower(result), "."))
    
    if (!(grepl("Protection could therefore be positively impacting this variable", result))) {
      # No sig dif between the two
      desired <- sub(".*\\s+", "", pillar_ecol_df$scoring[indicator_keep])
      actual_results <- ifelse(grepl("increase", sub("\\..*", ".", pillar_ecol_df$trend_statement[indicator_keep])), "increase", "decrease")
      
      if (pval > 0.05) { ## This is pval of the variable (not inside/ outside)
        cat("The rate in which this indicator is changing is not significant (p=", pval,") which suggests that climate change does not seem to have a significant impact on that particular indicator.")
      } else {
        # change is significant
        if (identical(desired, actual_results)) {
          cat("The results show us that climate change doesn't seem to be impacting this indicator the way we would expect, and in fact, the trends are showing a statistically significant trend in the opposite direction than we would expect.")
        } else {
          #The trend is going in the opposite direction that we would expect and
          #statistically significant,we point out that according to our analysis
          cat("The results show us that climate change could be impacting this indicator the way we would expect, and in fact, the trends are showing a statistically significant
        trend in the direction than we would expect as a result of climate change.")
        }
      }
    }
    } else {
    cat("More sampling is suggested.")
  }
  }
  
  cat("\n\n")
}

cat("### Research Recommendations \n")
cat(paste0(
  "The following indicator bins do not have any data: ",
  paste0(summary_table$Indicator.Bin[which(summary_table$Grade == "NA")], collapse = ", "),
  ". It is recommended to further study these areas.\n"
))
cat("\n\n")

# Bad grade table
badGrade <- which(pillar_ecol_df$areaID == state$mpas & (!(is.na(pillar_ecol_df$indicator))) & (!(pillar_ecol_df$indicator == "placeholder")) & (!(grepl('Inside Outside', pillar_ecol_df$indicator))) & (pillar_ecol_df$score < 51 | is.na(pillar_ecol_df$score)))

badGradeTable <- pillar_ecol_df[badGrade, ] |> 
  dplyr::group_by(bin) |>
  dplyr::ungroup() |>
  dplyr::select("indicator", "score")


cat("The following indicators are scoring low or don't have enough data to properly score. Some additional effort should be considered with these indicators: \n")

print(knitr::kable(badGradeTable, caption = "Indicator to Potentially Further Explore",row.names=FALSE))


```








## Collaborations and partnerships


```{r, echo=FALSE, warning=FALSE, error=FALSE, results="asis"}
project_subset <- pillar_ecol_df$PPTID[which(pillar_ecol_df$areaID == state$mpas)]
if (!(length(project_subset) == 0)) {
p_subset <- unique(trimws(unlist(strsplit(project_subset, ";")), "both"))
}
if (any(is.na(p_subset))) {
  p_subset <- p_subset[-which(is.na(p_subset))]
}
if (any(p_subset == "NA")) {
  p_subset <- p_subset[-which(p_subset == "NA")]
}

if (any(p_subset %in% collaborations$project_id)) {
  good_col <- which(collaborations$project_id %in% p_subset)
  collab_subset <- collaborations[good_col,]
  
  ## For collaborations, I need to obtain the year. This would allow me to say 'for this year, x collaborations happened, but in previous years for this project, Y collaborations have happened).
  
  #last_year <- paste0((as.numeric(format(Sys.time(), "%Y"))-1),"-", format(Sys.time(), "%Y"))
  
  year_keep <- which(collab_subset$fiscal_year == last_year)
  
  if (!(length(year_keep) == 0)) {
    recent_col <- collab_subset[year_keep, !(names(collab_subset) %in% c("project_year_id", "new_or_existing", "type", "critical"))]
    names(recent_col) <- c("Project ID", "Organization", "Year")

   organizations <- unique(recent_col$Organization)
    rc <- data.frame(Organization=organizations)
    
    for (i in seq_along(organizations)) {
      keeping <- which(recent_col$Organization == organizations[i])
      rc$Year[i] <- paste0(sort(unique(recent_col[keeping,]$Year)), collapse= ", ")
    }
    cat(paste0("The following collaborations/partnerships were identified for ", last_year, " for projects that contributed to this site:"))
    cat("\n\n")

    print(knitr::kable(rc, caption = "Recent Collaborations and Partnerships",row.names=FALSE))
    cat("\n\n")
  } else {
  cat(paste0("In year ", last_year, " there were no identified collaborations/ partnerships. /n/n"))  
  }
  if (!(length(which((!(1:length(collab_subset$project_id)%in% year_keep))))) == 0) {
    
    cat("The following past partnerships/collaborations have been identified and contributed to this site: \n\n")
    past_coll <- collab_subset[-year_keep, !(names(collab_subset) %in% c("project_year_id", "new_or_existing", "type", "critical"))]
    names(past_coll) <- c("Project ID", "Organization", "Year")
    organizations <- unique(past_coll$Organization)
    pc <- data.frame(Organization=organizations)
    
    for (i in seq_along(organizations)) {
      keeping <- which(past_coll$Organization == organizations[i])
      pc$Year[i] <- paste0(sort(unique(past_coll[keeping,]$Year)), collapse= ", ")
    }

    print(knitr::kable(pc, caption = "Past Collaborations and Partnerships",row.names=FALSE))
    
  } else {
    cat("There are no partnerships/collaborations identified from previous years. \n\n")
  }
} else {
    cat("There have been no identified collaborations/ partnerships for this area using the Project Planning Tool. \n\n")
}
```

## Outreach and engagement

### Deliverables

```{r, echo=FALSE, error=FALSE, warning=FALSE, results='asis'}
deliv_keep <- which(deliverables$project_id %in% p_subset & deliverables$year == last_year) # Only projects for this area / last year

if (length(deliv_keep > 0)) {
  delv <- deliverables[deliv_keep,][c("classification_display", "description")]
  if (any(str_count(delv$description, "\\S+") > 35)) {
  delv$description[which(str_count(delv$description, "\\S+") > 35)] <- " "
  }
  
  names(delv) <- c("Deliverable", "Description")
  
  print(knitr::kable(delv, caption = paste0("Deliverables for " , last_year ),row.names=FALSE))
} else {
  cat("There has been no identified deliverables in the Project Planning Tool for projects supporting this area.")
}

```

### CSAS

```{r, echo=FALSE, error=FALSE, warning=FALSE, results='asis'}
# Which ones to keep
csas_keep <- which(grepl(paste(state$mpas, collapse = "|"), csas$title)) # state$mpas
if (state$mpas == "Western and Emerald Banks Marine Refuge") {
csas_keep <- c(csas_keep, which(grepl("Emerald Banks", csas$title, ignore.case=TRUE)))
} else if (state$mpas ==  "St. Anns Bank Marine Protected Area") {
  csas_keep <- c(csas_keep, which(grepl("Anns", csas$title, ignore.case=TRUE)))
} else if (state$mpas == "Musquash Estuary Marine Protected Area") {
  csas_keep <- c(csas_keep, which(grepl("Musquash", csas$title, ignore.case=TRUE)))
}

if (length(csas_keep) > 0) {
  CSAS <- csas[csas_keep,]
  names(CSAS) <- c("Title", "Date")
  print(knitr::kable(CSAS, caption = paste0("CSAS Processes for " , state$mpas),row.names=FALSE))
} else {
  cat("There have been no identified relevant CSAS meetings in the CSAS DMapps related to this area.")
}




```

